### 2016-03-20 section/5_exper.tex
check in comparison with other techniques and explanation why we only use 21 bugs from Toddler

Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
We re-implement these basic data structures following one recent version of openjdk. 
We re-implement the buggy codes and test inputs in the bug reports, 
following the original data flow and control flow dependence. 
For two benchmarks, there are only 4 loops in our re-implemented versions. 
For all other benchmarks, there are no less than 5 loops.} 
Note that, Toddler focuses on inefficient nested loops, and its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.
We use Toddler benchmark suite because it provides a large set of
repeatable inefficient loop problems.

@@

As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
false positive and 23 benign false positives for all the top 5 loops
of the \allbugs benchmarks.

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 11 out of the
13 benign cases (XXX subject to change XXX). 
In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.
The remaining cases XXX.

The accuracy of \Tool benefits from its run-time analysis.
For example, there are 7 (XXX to change XXX) benchmarks in total that each contains
a loop that generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies 3 (XXX to change XXX) of them as truly inefficient and severe enough
to cause the corresponding performance problem.

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking. 
XXX

@@

\subsection{Comparison with other tools}
XXXXXX

>>>>

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
{\color{red}
Second, we evaluate \Tool on bugs from Toddler~\cite{Alabama, toddlerbuglist} project.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 performance bugs that have been fixed by developers. We evaluate \Tool on all these 21 bugs.
All of these bugs come from Java programs.
All these bugs are related to misusing basic data structures in Java, like ArrayList, HashSet, HashMap, and LinkedList. 
We re-implement these basic data structures following one recent version of openjdk. 
We re-implement the buggy codes and test inputs in the bug reports, 
following the original data flow and control flow dependence. 
For two benchmarks, there are only 4 loops in our re-implemented versions. 
For all other benchmarks, there are no less than 5 loops.
Note that, Toddler focuses on inefficient nested loops, and its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.
We use Toddler benchmark suite because it provides a large set of
repeatable inefficient loop problems. 
}

@@

As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
false positive and 22 benign false positives for all the top 5 loops
of the \allbugs benchmarks.

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. {\color{red} This happens to 20 out of the
22 benign cases.} % 11 out of 13 in the first benchmark set 
In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
{\color{red} For example, there are 26 % 7 in the first benchmark set
benchmarks in total that each contains
a loop that generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies 21 %3 in the first benchmark set 
of them as truly inefficient and severe enough
to cause the corresponding performance problem.
}

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking. 
%XXX

@@

\subsection{Comparison with other tools}

{\color{red}
\cite{Alabama, CARAMEL, IsilDillig.PLDI15} are most recent performance bug detection techniques. 
These techniques aim to find previously unknown performance bugs inside programs. 
Compared with diagnosis techniques, they do not consider real-world workload, 
and they are likely to report performance bugs without user-perceived symptoms.

Toddler~\cite{Alabama} tries to identify redundant computation through monitoring repetitive memory access patterns. 
21 out of 45 bugs in our benchmark set can be detected by Toddler, 
and 12 out of 18 bugs used in our evaluation can be detected by Toddler. 
All these bugs contain a loop traversing the same data structure many times, 
including all cross-loop redundant bugs and part of resultless bugs. 
Except for cross-loop redundant bugs, Toddler does not provide more information than fault localization. 
Compared with LDoctor, Toddler will incur a large runtime overhead, 
because it monitors all memory read instructions, 
and Toddler will report more false positives, because our cross-loop redundancy algorithm is more strict.

Caramel~\cite{CARAMEL} can statically detect loops with Cond-Break Fix. 
Caramel cannot detect any bug in our benchmark set, 
and Caramel cannot detect any bugs from Toddler benchmark set either. 
Depending on the dynamic workload, bugs detected by caramel can be identified as resultless loops or missed by LDoctor.

CLARITY~\cite{IsilDillig.PLDI15} can statically detect redundant traversal bugs. 
Compared with Toddler, the traversed data structures are not changed across different instances of the buggy loop. 
CLARITY can detect 6 out of 45 bugs in benchmark set, and can detect 5 out of 18 bugs evaluated in our experiment. 
CLARITY can detect 14 out of 21 bugs in TODDLER benchmark set used in our experiment, 
and all these bugs belong to RetainAll and ContainAll cases discussed in~\cite{IsilDillig.PLDI15}.
}
